Information Distribution Depends on Language-Specific Features

### 2019-01-30 cogsci/position-info.Rmd

```{r plot_bnc_and_switchboard}
ggplot(switchboard_entropies, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  geom_pointrange() +
  geom_smooth(se = F)

@@

We used the Providence English corpus from CHILDES. The Providence corpus recorded interactions between children between 1 and 3 years old and their parents in the home. We divided the corpus by speaker into child and non-child categories. We further divided the corpus by utterance length, so that all sentences of length $k$ (e.g. $6$) were grouped together. Finally, within each utterance length, we computed the unigram entropy measure for each position.

The entropy curves capture individual variation across positions in utterances of the same length. This allows us to directly observe and judge the amount of variation in words that appear in an individual position of a sentence. For speech data, which for the corpora in the CHILDES database consists of short and often disconnected utterances across hours of recordings, the unigram entropy measure is unaffected by context or lack thereof in utterances by the adults and children in the corpora. We can directly compare any two positions within utterances to determine the amount of uncertainty, and therefore information, on average contained by words within that position of utterances. We are applying the same approach as in @genzel2002, but within sentences instead of across sentences.

>>>>

```{r plot_bnc_and_switchboard}
ggplot(switchboard_entropies, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  ggtitle("Representative Switchboard Entropy Curves Faceted on Utterance Length") + 
  xlab("Word Order within Utterance") +
  ylab("Positional Entropy") +
  scale_x_discrete(limits = "1":"9") + 
  geom_pointrange() +
  geom_smooth(se = F)

@@

# Experiment 2

We used the Providence English corpus from CHILDES. The Providence corpus recorded interactions between children between 1 and 3 years old and their parents in the home. For speech data, which for the corpora in the CHILDES database consists of short and often disconnected utterances across hours of recordings, the unigram entropy measure is unaffected by context or lack thereof in utterances by the adults and children in the corpora.We divided the corpus by speaker into child and non-child categories. We further divided the corpus by utterance length, so that all sentences of length $k$ (e.g. $6$) were grouped together. Finally, within each utterance length, we computed the unigram entropy measure for each position. Computation of positional entropy was identical to the Switchboard method after dividing for utterance length.
